---
title: "Twitter API Analysis"
author: Jessica Moore, Binghai Ling
output: pdf_document
---

[[Why social media/twitter is important]]. Twitter, a free service that allows individuals to publicly broadcast 140-character messages (called "tweets"), is one such social media site. At the beginning of 2016, Twitter had roughly 310 million users.^1^ We analyzed the total number of tweets that were sent in a given 24-hour period. We also analyzed the total number of tweets containing the term "coffee" that were sent in a different 24-hour period.

Below, we show the total number of tweets we observed between [[]] and [[]].

```{r, echo=FALSE}
#unfiltered twitter data
```

Below, we show the total number of tweets containing the term "coffee" that we observed between [[]] and [[]].

```{r, echo=FALSE}
#filtered twitter data
```

[[Analysis]]

There are a few important caveats to our methodology. First and foremost, we have only obtained a sample of all tweets sent during the two 24-hour periods we analyzed. While we believe that the sampling mechanism scales the number of tweets with the number of tweets sent, we would have difficulty verifying this without delving further into the Twitter API. If the ratio between the number of tweets sampled and the number of tweets sent changes over time, our analysis [[would be very wrong]]. Secondly, [[]]. Finally, [[]].

[1] Statista, The Statistics Portal. "Number of monthly active Twitter users worldwide from 1st quarter 2010 to 2nd quarter 2016 (in millions)". Accessed: Sept. 29, 2016. https://www.statista.com/statistics/282087/number-of-monthly-active-twitter-users/.